\section{Kolmogorov extension theorem}
Assume $X$ is a set and $(\B_n)_{n=1}^\infty$ is an increasing sequence of $\sigma$-algebras of subsets of $X$. Assume $\mu_n$ is a measure on $(X,\B_n)$ and 
\[\left. \mu_{n+1} \right|_{\B_n}=\mu_n,\hspace{4mm}\forall n.\]
Can we define a measure $\mu$ on $(X,\B)$, where $\B=\sigma\left(\bigcup_{n=1}^\infty \B_n\right)$ s.t. $\left.\mu\right|_{\B_n}=\mu_n$, $\forall n$?
In general \underline{no}. But we have the following:

\begin{theorem}

    In the above setting, assume in addition that $\mu_n(X)=1$ $\forall n$ and there is a collection of subsets $\CC\subset \B$ s.t.:
    \begin{enumerate}
        \item $\mu_n(A)=\sup\{\mu_n(C)\omm: \omm C\subset A, C\in \CC\cap \B_n \}$ $\forall A\in \B_n$,
        \item if $(C_n)_{n=1}^\infty$ is a sequence in $\CC$ and $\cap_{n=1}^\infty C_n=\emptyset$, then $\cap_{n=1}^N C_n =\emptyset$ for some $N$.
    \end{enumerate}
    Then there is a unique measure $\mu$ on $(X,\B)$ s.t. $\left.\mu\right|_{\B_n}=\mu_n$.
\end{theorem}

\begin{remark}

    If in addition $\CC$ is closed under finite unions and countable intersections, then 
    \[\mu(A)=\sup\{\mu(C)\omm:\omm C\subset A, C\in \CC\}\hspace{4mm}\forall A\in\B.\]
    Indeed, consider the collection $\tilde\B$ of sets $A\in \B$ s.t. 
    \begin{align*}
        \mu(A)= & \sup\{\mu(C)\omm:\omm C\subset A, C\in \CC\},\\
        \mu(A^c)= & \sup\{\mu(C)\omm:\omm C\subset A^c, C\in \CC\}.
    \end{align*}
    Then $\tilde\B$ is a $\sigma$-algebra by the same argument as in the lecture on regularity of measures, and $A\subset \tilde \B$. Hence, $\tilde \B = \B$.
\end{remark}

Assume now we have a collection $((X_i,\B_i))_{i\in I}$ of measurable spaces, (It can be infinite and uncountable). Consider $X=\prod_{i\in I} X_i.$
Denote by $\prod_{i\in I} \B_i$ the $\sigma$-algebra generated by all sets of the form \[\prod_{i\in I} A-i \times \prod_{j\in F^c} X_j,\]
where $F\subset I$ is finite, $A_i\subset \B_i,\hspace{2mm} (i\in F)$.

\begin{example}

    Consider a sequence $((X_n,d_n))_{n=1}^\infty$ of separable metric spaces. We assume $d_n(x,y)\leq 1,\hspace{3mm}\forall x,y$. Note that any metric can be replaced by definition
    $\tilde d(x,y) = d(x,y)/(1+d(x,y))$. Then $\prod_{n\in I} X_n$ is a metric space with metric \[ d(\ux,\uy)=\sum_{n=1}^\infty \frac{1}{2^n}d_n(x_n,y_n), \]
    where $\ux = (x_n)_{n=1}^\infty\in X$. Given a sequence $(\ux(n))_{n=1}^\infty$ in $X$, we have $\ux(n)\xrightarrow[n\rightarrow\infty]{}\ux$ if and only if $x(n)_k\xrightarrow[n\rightarrow\infty]{}x_k,\hspace{2mm} \forall k$.
    Consider the Borel $\sigma$-algebra $\B(X_n)$. Then $\prod_{n=1}^\infty \B(X_n)=\B(X)$.

    To see this, for every $n$, choose open sets, $U_{nk}\subset X_n$ $(k=1,2,...)$ s.t. every open set in $X_n$ is the union of some of $U_{nk}$'s. This is possible by 
    separability. Take a dense countable subset of $X_n$ and then all balls of rational radii with centers at points of this subset. Then every open subset of $X$ is the 
    union of sets of the form 
    
    \[U_{1,k_1}\times U_{2,k_2}\times\ldots\times U_{n,k_n}\times \prod_{m=n+1}^\infty X_m.\]
    Therefore, such sets generate the $\sigma$-algebra $\B(X)$, and as $U_{n,k}$ $(n\in \N)$ generate $\B(X_n)$, we conclude that $\cap_{n=1}^\infty \B(X_n)=\B(X).$
\end{example}

\begin{remark}
    In relation to this example, we will need the following:
\end{remark}

\begin{theorem}(\underline{\textbf{Tychonoff}})
    
    Assume $((X_n,d_n))_{n=1}^\infty$ is a sequence of compact metric spaces. Then $\prod_{n=1}^\infty X_n$ (with metrics as in the example) is compact. 
\end{theorem}

\begin{theorem}(\underline{\textbf{Kolmogorov extension theorem}})\\
    Assume $(X_i)_{i\in I}$ is a collection of metric spaces. Consider $X=\prod_{i\in I} X_i$, $\B=\prod_{i\in I} \B(X_i)$. Assume for every finite $F\subset I$ we are given 
    a regular Borel probability measure $\mu_F$ on $X_F$ s.t. 

    \[(\pi_{G,F})_*\mu_G = \mu_F\]
    for all finite $F\subset G\subset I$. Then there is a unique probability measure $\mu$ on $(X,\B)$ s.t. 
    
    \[(\pi_{I,F})_*\mu=\mu_F\]
    for all finite $F\subset I$.
    
\end{theorem}

\begin{remark}
    
    If in addition the spaces $X_i$ are separable, then we can also conclude that for every $A\in \B=\prod_{i\in I}\B(X_i)$ we have 

    \[\mu(A)=\sup\mu(C),\]
    where the supremum is taken over the sets $C\subset A$ of the form \[ C= K \times \prod_{i\in I\backslash J}X_i,\]
    where $J\subset I$ is countable and $K\subset X_J$ is compact.  
\end{remark}